%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/kevinaiken}{\Large Kevin Aiken}} & Email : \href{mailto:aiken.kevin.m@gmail.com}{aiken.kevin.m@gmail.com}\\
  \href{https://github.com/kevinaiken}{https://github.com/kevinaiken} & Mobile : +1-770-773-6538 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia State University}{Atlanta, GA}
      {Bachelor of Science in Computer Science;  GPA: 3.6}{Aug. 2016 -- May. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {NCR}{Atlanta, GA}
      {Software Engineer}{July 2019 - Present}
      \resumeItemListStart
      \resumeItem{Technical Leadership}
        {Led a team of software engineers and quality engineers, planning our roadmap and executing on it, while also growing junior members of the team.}
      \resumeItem{Vagrant}
        {Significantly updated our Vagrant and SaltStack based virtualization infrastructure to generate virtual labs more effectively.}
      \resumeItem{Python Integration Testing}
        {Designed and implemented a Python Integration testing framework to orchestrate complex system tests on distributed systems.}
      \resumeItem{Task Automation}
        {Maintained and improved several Python based utilities designed to automate previously manual tasks, such as re-imaging labs.}
    \resumeItemListEnd

    \resumeSubheading
      {OttoDock}{Dawsonville, GA}
      {Software Engineer}{Oct. 2018 - Present}
      \resumeItemListStart
        \resumeItem{Product Development}
          {Worked with a multidisciplinary group of engineers to design a concept for autonomous lake docks that self position and provide a variety of smart features, and then iterated through several prototypes. Currently we have a handful of beta docks in the water at Lake Lanier.}
        \resumeItem{Backend}
          {Developed the Kotlin+Spring backend from the ground up. It currently consists of many API's for CRUD operations, websockets for live video and data streaming, and a variety of scheduled tasks.}
        \resumeItem{Infrastructure}
          {Implemented and refined our approach to cloud infrastructure on AWS following best practices, including fully implemented CI/CD.}
        \resumeItem{Security}
          {Researched and implemented our security approach, following best practices to implement user login, password reset, and authentication on both API's and websocket connections.}
        \resumeItem{Project Management}
          {Helped scale our approach to work as we grew larger, using Github projects and Agile concepts to build our product more effectively.}
      \resumeItemListEnd

    \resumeSubheading
      {T-Mobile}{Dunwoody, GA}
      {Software Engineering Intern}{June 2018 - May 2019}
      \resumeItemListStart
        \resumeItem{Full Stack Development}
          {Developed several full stack applications using Angular and Java Spring to demonstrate concepts.}
        \resumeItem{Backend Mocking}
          {Virtualized a financial backend service to simulate partial system outages so that the behavior of our application could be thoroughly validated.}
        \resumeItem{Kubernetes Prototyping}
          {Prototyped a proof of concept to run a document signing application on Kubernetes to increase the performance and robustness of the application. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{MarkIt}
      {Hackathon project using web NFC to to implement checkout-less shopping}
    \resumeSubItem{IoT Physical Therapy}
      {Worked with a professor in Georgia State's Physical Therapy Department to provide them a specifically tailored Android application for conducting physical therapy on participants using Myo EMG bands.}
    \resumeSubItem{Undergraduate Research}
      {Prototyped an automated personnel tracking solution using both passive bluetooth sampling and streaming cloud computer vision.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Kotlin, Python, Java, SQL}
      \hfill
      \textbf{Technologies}{: AWS, Linux, Vagrant, SaltStack, Jenkins, Spring}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
